Improving \textsl{Gaia} parallaxes with a data-driven model of the color--magnitude diagram

### 2017-02-22 paperDistance/paper.tex
discussion content

\section{Discussion}
What have we achieved and why is it important?

@@

>>>>

\section{Discussion}

We have shown that it is possible to obtain photometric parallaxes for
distant stars in the \gaia\ data without any use of physical stellar
models.
Although we have not performed principled Bayesian inference in this
project, we have performed a statistically responsible deconvolution
of the \gaia\ \tgas\ data that is justifiable under a clear set of
assumptions.
This deconvolution makes use of a reasonable noise model and an
assumption of stationarity to shrink the parallax uncertainties, and
do so dramatically for the stars measured at lower signal-to-noise.
Because the model we use (Extreme Deconvolution or XD) accounts for
heteroskedastic noise, we were able to build our photometric parallax
model---which is a model of the color--magnitude diagram (CMD)---using
all the data, not just the data with the highest signal-to-noise or
largest parallaxes.
That is, the model for the CMD we have built is representative for
the \tgas\ Catalog.
Inasmuch as that is true, we expect the distance estimates to be
weakly biased.

What would be different if we wanted a model not of the \tgas\ data,
but a model appropriate for the full billion stars, or for a
volume-limited sample of stars?
How could we convert our existing results?
How would we do it properly in general?

@@

How this compares to other Bayesian attempts at inferring distances,
like, eg, the Tri--Coryn papers. Favorably! And with \emph{fewer}
assumptions, in fact!
